Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/table_differential.tex
pass on table_differential
pass on issues

    \midrule
    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & &
    \veight{} & \textbf{Confirmed} &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
    & 2 &  & \\
    \midrule

    15 & 8/23 & quickfuzz & \jsc{} & New  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
    & - & \hi{} & Test262\\
    16 & 8/23 & quickfuzz & \veight{} & New  &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
    & - & \hi{} & Test262\\

>>>>

    \midrule
    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & &
    \veight{} & \textbf{Fixed} &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
    & 2 &  & \\
    \midrule

    15 & 8/23 & quickfuzz & \jsc{} & New  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
    & - & \hi{} & Test262\\
    16 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
    & 2 & \hi{} & Test262\\
